
This long lived Ph.D. has initiated its roots in formation flying of satellites, had a short affair with aircraft trajectory estimation in presence of shared wind information end hopefully dies in the hands of heat transfer enhancement via utilizing magnetic nanofluids.  
Along the way, a lot of people has contributed some way or another, but the first one to mention is my advisor for the final station, Prof. Dr.  \.{I]}brahim \"{O}ZKOL. First of all, I am grateful to have an advisor to back me up, with a fatherly manner, understanding and cheerful. His guidance led me to this point, I can not thank him enough. 

And then comes Asc. Prof. G\"uven K\"{O}M\"URG\"{O}Z KIRI\c{S}, although not officially my co-advisor, she was much more than that. Her support on this work is may be more than anyone, not even mentioning her friendly attitude.. 

My family, my mom Nergiz and father Adiguzel, I am grateful to you most, for the most precious gift you gave me, my life. Mom, you are the reason of my freedom, my imagination and my free will. I always admired you being competent since I first saw you at work, passionately talking on your profession, eyes closed, hard to believe that it was my mother. 

And dad, you are the reason for my artistic spirit, which tries to burst out of me sometimes. You both always supported me on music, always supported my choices, I was lucky to be grown as a free spirit, I think this is where I am grateful the most. 

My brother, you are really special to me. It is enough to make me happy just knowing you are there.

My grandmom, nananem. The cleverest women I have ever known, lucky to be raised by you. I wont forget that you being the person that I get along the best, never even an argument, like magic. My flees to captains bridge has never been punished on the way along the sea to summer house, my never finishing questions never left unanswered, my passion for sea shells and flower seeds plugging the washing machines have been ignored. 

My uncle Cengiz, where my logic genes have been inherited. Again, the person I have never argued even once in my lifetime, no delays in communication, or may be sometimes when something else has been processed. The best person I have ever known in my life, an angel. Too clever, too talented. And aunt Leyla, woke me up everyday, patiently, thank you many times.

Rapunzel, my companion, you have lived your most of your life during this thesis. Although you wont be able to read it, you wont be the first one. 

Ertan, you have helped me numerous times I stopped counting, my crisis, my anxieties, my vulnerabilities. Those days I was about to quit, you made me back, not let me to leave Rapunzel, told me that I can do it, and I did it. 

Ellie Arroway, my hero for Aero&Astro, most probably the biggest reason that I am here, although not very logic. one down.. a couple million to go.. 

Utku, ne 3 u la, my perfect lab mate. Hope to work AI together here or there, one day.. 

The drone team in ENAC, with whom my last three years passed. Best team ever. Felt like home. Thank you all..